---
title: "Activity 2 - Day 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task2 : Loading the necessary packages

```{r Loading_packages}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(tidymodels))
suppressPackageStartupMessages(library(GGally))

```

## Task3 : Loading the data

```{r Loading_dataset}
hfi<-readr::read_csv("https://www.openintro.org/data/csv/hfi.csv",show_col_types = FALSE)
```

1) This is an observational study as it was not using or conducting any experiment to produce the reports. 

## Plot to visualize the distribution of pf_score

```{r}
plot1 <- hfi %>% ggplot(aes(x=pf_score))+
  geom_histogram(fill="dodgerblue",color="black")+
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks = c(0,20,40,60,80,100))+
  theme_bw()

plot1
```

2) The univariate histogram for pf_score is left_skewed with extreme outliers on the left (very low pf_scores) and multiple peaks. I expected that a lot of countries will be having low pf_scores but surprisingly it was the opposite.


3) I have decided to describe the relation between pf_rol_civil and pf_rol_criminal which looks Linear relationship for me and displayed below with the help of a scatter plot and linear regression line.

```{r}
plot2<- hfi %>% ggplot(aes(x=pf_rol_criminal,y=pf_rol_civil))+
  geom_point(color="red")+
  geom_smooth(method = lm)+
  theme_bw()

plot2
```

# Task4 : Pairwise relationships

```{r,warning=FALSE}
hfi %>% 
  select(ends_with("_score")) %>% 
  ggpairs()
```


4)  - hf_score and pf_score -  strong Linear relationship
    - hf_score and ef_score -  moderate Linear relationship
    - pf_score and ef_score -  no relationship (nuetral)
    
5)  - hf_score and pf_score are highly correlated with correlation-coefficient of 0.943
    - hf_score and ef_score are highly correlated with correlation-coefficient of 0.855
    - ef_score and pf_score are moderately correlated with correlation-coefficient of 0.633
    
## Task5 : The Multiple Linear Regression Model

```{r}
m_hr_ef <- lm(pf_score ~ hf_score + ef_score, data = hfi)
tidy(m_hr_ef)
```

6) The estimated equation for this model is

$$
\texttt{pf_score} = (1.464213e-11) + (2.000000e+00) \times \texttt{hf_score} + (-1.000000e+00) \times \texttt{ef_score} + \varepsilon
$$


**I am done for the day**


